Methods for Analyzing Models of Rod-Shaped Bacteria

### 2025-07-27 paper/main.tex
rename sections
remove label
add citation as reminder
insert citation

% --------------------------------------------------------------------------------------------------
\subsubsection{Relationship to Semantic Segmentation (TODO)}
\label{paragraph:comparison-semantic-segmentation}
\cite{Jadon2020}

@@

%###################################################################################################
\section{A Mechanical Model for Rod-Shaped Bacteria}
\label{subsubsection:mechanical-model-rod-shaped-bacteria}

@@

While some rod-shaped bacteria grow by inserting new material at the ends, \textit{E.Coli} and
\textit{B.Subtilis} utilize a method where new material is inserted along the cylindrical part of
the rod.
The details of the division event (i.e. Z-Ring formation) are very intricate and are heavily
studied as a subject on their own (TODO citation).
On a higher level view, the rod is split apart at a point close to the center of the cell, thus
creating two new daughter cells.
We know that the best predictor for when the division event occurs, is the length of the rod as
opposed to the age of bacterium~\cite{Robert2014}.
Furthermore, only the growth of the whole colony but also the individual growth of the bacteria is
exponential~\cite{Amir2014,Takeuchi2005}.

@@

%###################################################################################################
\section{Parameter Estimation of \textit{E.Coli.} growing on Agar}
% --------------------------------------------------------------------------------------------------
\subsection{Data Preparation}
TODO: Decide if this should be Supplement
\begin{enumerate}
    \item Have masks of data; reference image segmantation tools; or do it by hand
    \item ensure that colors are matching for bacteria between time-steps
    \item clean borders of images if needed
    \item know domain size; otherwise use pixels
\end{enumerate}

@@

>>>>

% --------------------------------------------------------------------------------------------------
\subsubsection{Relationship to Semantic Segmentation (TODO)}
\cite{Jadon2020}

@@

%###################################################################################################
\section{A Computational Model for Rod-Shaped Bacteria}
\label{subsubsection:mechanical-model-rod-shaped-bacteria}

@@

While some rod-shaped bacteria grow by inserting new material at the ends, \textit{E.Coli} and
\textit{B.Subtilis} utilize a method where new material is inserted along the cylindrical part of
the rod.
The details of the division event (i.e. Z-Ring formation) are very intricate and are heavily
studied as a subject on their own~\cite{Harry2001}.
On a higher level view, the rod is split apart at a point close to the center of the cell, thus
creating two new daughter cells.
We know that the best predictor for when the division event occurs, is the length of the rod as
opposed to the age of bacterium~\cite{Robert2014}.
Furthermore, only the growth of the whole colony but also the individual growth of the bacteria is
exponential~\cite{Amir2014,Takeuchi2005}.

@@

%###################################################################################################
\section{Application to \textit{E.Coli.} growing on Agar (TODO)}
% --------------------------------------------------------------------------------------------------
\subsection{Data Preparation}
TODO: Decide if this should be Supplement
\begin{enumerate}
    \item Have masks of data; reference image segmantation tools; or do it by hand
    \item ensure that colors are matching for bacteria between time-steps
    \item clean borders of images if needed
    \item know domain size; otherwise use pixels
\end{enumerate}

@@

\cite{You2019}
